Analyzing the Effectiveness of Copyright Law on AI Output in Software Engineering and Future Developments

### 2025-02-18 paper/main.tex
done with paper

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
TODO: need to do this later
\end{abstract}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
  The increasing usage of code-generation tools by the developer community
  has not considered the legal implications of using AI-generated code. With
  model training data known to be publicly sourced, the chances of
  generated code being tied to licensed code are large. New research shows that
  origin analysis can be performed on the generated code to find its author/host
  repository which could make way for legal proceedings.

\end{abstract}
